### 2020-10-08 input/background.tex
figure of simple add

\begin{figure*}
  \begin{center}
    \subfloat[Part A]{\label{fig:addA}Meow}{input/figaddA.tex}
    \hspace{5pt}
    \subfloat[Part A]{\label{fig:addA}Meow}{input/figaddA.tex}
  \end{center}
\end{figure*}

Transitive relationships ensure that each process gets its closest
source while accumulators ensure that messages propagation
terminates. The system converges towards the optimal partitioning
despite processes not broadcasting all messages. Removals of
partitions are more challenging. \TODO{Figure.} One could solve this
issue by removing partitions that were not advertised for a defined
time~\REF. However, relying on physical timeout could lead to either
premature removals of partitions when they are still operating; or
slow convergence where processes believe they belong to a partition
that was removed.

>>>>

\begin{figure*}
  \begin{center}
    \subfloat[Part A][\label{fig:addA}Both Process $a$ and
      Process $c$ initiate a partition.
      $w_{ab} = 1.5$; $w_{bc} = w_{cd} = w_{bd} = 1$.]{\input{input/figaddA.tex}}
    \hspace{5pt}
    \subfloat[Part B][\label{fig:addB}Messages transit through communication
      links and carry increasing weights.]{\input{input/figaddB.tex}}
    \hspace{5pt}
    \subfloat[Part C][\label{fig:addC}Process $b$ receives and forwards
      $Add_{c, +1}$ then discards $Add_{a, +1.5}$, for the latter distance
      is higher.]{\input{input/figaddC.tex}}
    \hspace{5pt}
    \subfloat[Part D][\label{fig:addD}Processes $b$, $c$, and $d$ discard
      incoming messages. The system converged to optimal partitions.]{
      \input{input/figaddD.tex}}
    \caption{\label{fig:add}Simple accumulation in messages makes the
      system converge to optimal partitions with contained
      flooding.}
  \end{center}
\end{figure*}

Transitive relationships ensure that each process gets its closest
source while accumulators ensure that messages propagation
terminates. The system converges towards the optimal partitioning
despite processes not broadcasting all messages. Removals of
partitions are more challenging. \TODO{Figure.} \TODO{Also easy to
  solve when all processes receive all messages}. One could solve this
issue by removing partitions that were not advertised for a defined
time~\REF. However, relying on physical timeout could lead to either
premature removals of partitions when they are still operating; or
slow convergence where processes believe they belong to a partition
that was removed.
